---
title: "Switch-Over Analysis"
author: "Rudolph Santarromana"
date: "2023-09-26"
output: html_document
---
#Notes
```{r}
# Figure out how to use curtailment. I applied a price for electricity, but what about the curtailment values?
```


#Setup
```{r setup, include=FALSE}
#Initialize libraries and directory

library(tidyverse)
library(dplyr)
library(vroom)
library(peakRAM)
library(data.table)
library(readr)
library(pryr)
library(R2DT)
library(parallel)
library(beepr)
library(pillar)
library(ellipsis)
library(rlang)

# setwd("C:/Users/Rudolph/Desktop/Rudolph/0 - CMU - Portugal PhD Files/0 - Research/Transmission Switch Over")

finish <- function(n = 3) {
  for(i in 1:n){
    beep(1)
    Sys.sleep(0.5)
  }
  beep(5)
}

options(scipen = 999)
```

#CHECKPOINT
```{r SAVE and LOAD: Workspace - }
#Only the data tables are loaded using this workspace. All functions needed to generate these are not loaded.

save.image("C:/Users/Rudolph/Desktop/Rudolph/0 - CMU - Portugal PhD Files/0 - Research/Transmission Switch Over/Paper_3_Workspace.RData")

load("C:/Users/Rudolph/Desktop/Rudolph/0 - CMU - Portugal PhD Files/0 - Research/Transmission Switch Over/Paper_3_Workspace.RData")

```

```{r LCOE Function}
library(FinancialMath)

LCOE <- function(CAPEX, OPEX, ann.energy, r, life, lag = 0, type = 1, esc = 0.03) { #MEUR, MEUR/yr, MJ,  rate, lifetime, escalation factor 
  Inv <- CAPEX*1000000 #EUR
  Ann.V <- rep(1000000*OPEX,times = life) #EUR/yr
  escalation.factors <- (1 + esc)^(0:lag) #vector of escalation factors during building years
  E.F <- c(escalation.factors, rep(1, times = life)) #vector of escalation factors of entire project, including operation.
  if(lag == 0) { #if no lag
    CF <- c(Inv,Ann.V)
  } else {
    if(type == 1) {CF <- c(Inv, rep(0,times = lag), Ann.V)*E.F} #investment realized in year 0, and opex begins at start of life
    if(type == 2) {CF <- c(rep(Inv/(lag + 1), times = lag + 1), Ann.V)*E.F} #investment realized evenly over the lag period
    if(type == 3) { #investment realized in linearly growing increments starting at 5-10% in the first year
      cf.0 <- 0.05 #5% of CAPEX in the first year. This is typically the amount needed to secure the ITC.
      tot.add <- 1 + lag #this only works if deployment time is less than 20 years, otherwise we only spend 5% every year
      if(tot.add > 20) {stop("Lag is too long for this cashflow type")}
      add.V <- seq(0,lag) #the number of increments of the CF to be added each year
      CF <- rep(cf.0, times = lag + 1) #base CAPEX spend in each year
      increment <- ((1-sum(CF))/sum(add.V))*add.V #additional proportion that should be added each year
      CF <- CF + increment
      if(abs(sum(CF) - 1) > 0.00001) {stop("Error in type 3 cashflow")} #problem if the sum isn't close to 1
      else {CF <- c(CF*Inv, Ann.V)*E.F}
    }
    if(type == 4) { #investment randomly allocated over the development years
     CF <- runif(n = lag + 1) 
     CF <- CF/(sum(CF))
     if(abs(sum(CF) - 1) > 0.00001) {stop("Error in type 4 cashflow")} #problem if the sum isn't close to 1
     else{CF <- c(CF*Inv, Ann.V)*E.F}
    }
    # if(type != 1 | 2 | 3 | 4) {stop("Incorrect 'type' used")}
    } 
  times.V <- 0:(life + lag)
  NPV.CF <- sum(CF/(1+r)^times.V) #NPV in EUR
  
  if(ann.energy == FALSE) { #use this function to just calculate Net present cost
    LCOE <- round(NPV.CF,2) 
  } else {
    Ann.E <- c(rep(0, times = lag),rep(ann.energy, times = life)) 
    CF.E <- c(0,Ann.E)
    NPV.E <- sum(CF.E/(1+r)^times.V) #NPV in input unit
    
    LCOE <- round(NPV.CF/NPV.E,2)
  }
  
  
  return(LCOE) #returns value in EUR/(input unit)
}
```

```{r CHECK LCOE Function - DELETE}

(A <- LCOE(5,5,5,0.05,25,lag = 0, type = 1))
(B <- LCOE(5,5,5,0.05,25,lag = 0, type = 2))
(C <- LCOE(5,5,5,0.05,25,lag = 0, type = 3))
(D <- LCOE(5,5,5,0.05,25,lag = 0, type = 4))
```

```{r VISUALIZE Cash and energy flows}
Visual.CF <- function(CAPEX, OPEX, ann.energy, r, life, lag = 0, type = 1) { #MEUR, MEUR/yr, MJ,  rate, lifetime 
  Inv <- CAPEX
  Ann.V <- rep(OPEX, times = life)
}

```

```{r Calculate Curtailment Value, fig.width= 10, fig.asp= 0.5}
Curtailment <- function(plant.MW, cf, EUR.MWh = 60, lt = 20, dr = 0.05) {
  C.rate <- seq(1,8, by = 1) #percent of curtailed energy per year
  Gross.NRG <- plant.MW*8760*cf #in MWh/year
  C.NRG <- Gross.NRG*C.rate #in MWh/year of curtailed energy
  C.EUR <- C.NRG*EUR.MWh #in EUR/year value of curtailed energy
  
  C.NPV <- mapply(LCOE, CAPEX = 0, OPEX = C.EUR/1000000, ann.energy = FALSE, r = dr, life = lt)/1000000 #in MEUR over lifetime
  
  DF <- data.frame(Curtailment_Rate = C.rate, 
                   Curtailed_MWh = C.NRG,
                   Curtailed_MEUR = C.EUR/1000000,
                   Curtailed_NPV_MEUR = C.NPV)
  return(DF)
}

#Offshore wind typical
C.results <- Curtailment(1000,0.5,35, dr = 0.05)

# barplot(x = C.results$Curtailment_Rate, y = C.results$Curtailed_NPV_MEUR)

ggplot(data = C.results, aes(x = Curtailment_Rate, y = Curtailed_NPV_MEUR)) + 
  geom_bar(stat = "identity", fill = "steelblue") +
  labs(x = "Curtailment Rate [%]", y = "20-year NPV of Foregone Revenues [MEUR]") +
  theme(axis.text = element_text(size = 15)) +
  theme(axis.title = element_text (size = 15))

```

```{r Topology A: HVDC cable to shore}
Topology_A <- function(dist.km, plant.MW, cf = 0.5, EL.price = 35, r = 0.052, life = 25, curtailment = 0.05, interconnection = 3, CF.type = 2, ITC = 0, esc = 0.03) { #Follows Van Wingerden et al. (2023)
  ### Price of Energy (Assume it's just bought from a plant)
  Elec.Price <- EL.price #EUR/MWh. From IEA (2019) figure 7. 70% of the blue bar to exclude transmission
  
  ### Offshore Substation Platform
  # Platform.Inv <- 110000*plant.MW #EUR
  Platform.Inv <- 5840000 #EUR/platform. Assume one platform
  Platform.OPEX.pct <- 0.005 #% of investment
  Platform.OPEX.ann <- Platform.Inv*Platform.OPEX.pct #EUR/year
  
  ### Offshore substation (cost and efficiency)
  OSS.Inv <- 685000*plant.MW #EUR
  OSS.OPEX.pct <- 0.023 #% of investment per year
  OSS.OPEX.ann <- OSS.Inv*OSS.OPEX.pct ##EUR/year
  OSS.eff.pct <- 0.98
  
  ### Offshore Export Cable (cost and efficiency). Uses Xiang cable data
  HVDC.Cab = copy(HVDC.Cables)
  HVDC.Cab[ , N.Sets := ceiling(plant.MW/Circ.Capability.MW)]
  HVDC.Cab[ , Cab.CAPEX := Cost.EURMW_km * dist.km * plant.MW * N.Sets] #Returns value in EUR
  HVDC.Cab[ , Cab.EFF := mapply(HVDC.Eff, dist.km, plant.MW, .(Voltage.kV),.(Resistance.Ohkm),.(N.Sets))]
  
  Cab.Inv <- min(HVDC.Cab$Cab.CAPEX, na.rm = TRUE) #mean of the results from the cables. in EUR
  Cab.OPEX.pct <- 0.03 #% of investment per year
  Cab.OPEX.ann <- Cab.Inv*Cab.OPEX.pct  ##EUR/year
  Cab.eff.pct <- mean(HVDC.Cab$Cab.EFF, na.rm = TRUE)
  
  ### Onshore Substation
  NSS.Inv <- 200000*plant.MW #EUR
  NSS.OPEX.pct <- 0.015 
  NSS.OPEX.ann <- NSS.Inv*NSS.OPEX.pct ##EUR/year
  NSS.eff.pct <- 0.98
  
  
  Trans.MEUR_km <- ((Cab.Inv + NSS.Inv + OSS.Inv)/1000000)/dist.km #MEUR/km
  
  #Sums
  Total.Inv <- (1-ITC)*(Platform.Inv + OSS.Inv + NSS.Inv + Cab.Inv)/1000000 #MEUR
  Ann.OPEX <- (Platform.OPEX.ann + OSS.OPEX.ann + Cab.OPEX.ann + NSS.OPEX.ann)/1000000 #MEUR/year
  Tot.Eff <- OSS.eff.pct*Cab.eff.pct*NSS.eff.pct #percent
  Gross.NRG <- plant.MW*8760*cf #MWh/year of energy generated by OSW array
  Curt.NRG <- Gross.NRG*curtailment #MWh/year of curtailed energy
  Net.NRG <- (Gross.NRG - Curt.NRG)*Tot.Eff #MWh/year of energy delivered tos hore
  Net.NRG.Cost <- Gross.NRG*Elec.Price/1000000 #MEUR/year, assuming we are paying for the electricity generated by the array
  Tot.OPEX <- Ann.OPEX + Net.NRG.Cost #MEUR/year
  
  Levelized.Cost <- LCOE(Total.Inv, Tot.OPEX, Net.NRG, r, life, lag = interconnection, CF.type) #EUR/MWh
  Levelized.Cost.CAPEX <- LCOE(Total.Inv, OPEX = 0, ann.energy = Net.NRG, r, life, lag = interconnection, CF.type)
  Levelized.Cost.OPEX <- LCOE(CAPEX = 0, OPEX = Ann.OPEX, ann.energy = Net.NRG, r, life, lag = interconnection, CF.type)
  Levelized.Cost.EL <- LCOE(CAPEX = 0, OPEX = Net.NRG.Cost, ann.energy = Net.NRG, r , life, lag = interconnection, CF.type)
  
  return(data.frame(Investment = Total.Inv, Cable.MEUR_km = Trans.MEUR_km, OPEX = Ann.OPEX, LCOE.tot = Levelized.Cost, LCOE.CAPEX = Levelized.Cost.CAPEX, LCOE.OPEX = Levelized.Cost.OPEX, LCOE.EL = Levelized.Cost.EL, Efficiency = Tot.Eff, NRG_MWh = Net.NRG)) 
  #in MUSD/MW; USD/MJ
}

```

```{r Topology B: Offshore Electrolysis, H2 pipeline to shore}
Topology_B <- function(dist.km, plant.MW, cf = 0.5, EL.price = 35, PEM.price = 1926000, PIPE.price = 615, r = 0.052, PEM.eff = 0.642, life = 25, lag = 3, CF.type = 2) { #Follows Van Wingerden et al. (2023)
 H2.LHV <- 33.33 #kWh/kg or MWh/tonne 
 
 ### Price of Energy (Assume it's just bought from a plant)
  Elec.Price <- EL.price #EUR/MWh. From IEA (2019) figure 7. 70% of the blue bar to exclude transmission
  
  ### Offshore Substation Platform
  # Platform.Inv <- 110000*plant.MW #EUR
  Platform.Inv <- 5840000 #EUR/platform. Assume one platform
  Platform.OPEX.pct <- 0.005 #% of investment
  Platform.OPEX.ann <- Platform.Inv*Platform.OPEX.pct #EUR/year
  
  ### Offshore Electrolyzer (PEM)
  PEM.Inv <- PEM.price*plant.MW #EUR
  PEM.OPEX.pct <- 0.015
  PEM.OPEX.ann <- PEM.Inv*PEM.OPEX.pct #EUR/year
  PEM.eff.pct <- PEM.eff #% LHV 
  
  ### Offshore Desalination. Need 
  Desal.Inv <- 0*plant.MW #19260 #EUR. Take as 1% of the electrolyzer cost
  Desal.OPEX.pct <- 0 #CHECK
  Desal.OPEX.ann <- Desal.Inv*Desal.OPEX.pct #EUR/year
  Desal.eff.pct <- 1 #CHECK
  LCOH.Desal <- 0.04 #EUR/kgH2. ranges from 0.01 - 0.04 according to Megan Mauter email and IEA (2019) Future of Hydrogen Report.
  
  ### Offshore Compressor
  Compressor.Inv <- 15000*plant.MW #EUR
  Compressor.OPEX.pct <- 0.04
  Compressor.OPEX.ann <- Compressor.Inv*Compressor.OPEX.pct #EUR/year
  Compressor.eff.pct <- 0.985 #%
  
  ### Offshore Energy Storage (battery or fuel cell for black start). Need
  Storage.MW <- 0 #MW of battery needed. CHECK, how to estimate this?
  Storage.Inv <- 1000 #EUR/kW of battery needed. EIA Source for 1-hr battery pack: https://www.eia.gov/todayinenergy/detail.php?id=45596
  Storage.Inv <- 1000*Storage.MW*Storage.Inv #EUR 
  Storage.OPEX.pct <- 0.05 #Converted using the values from Dokhani et al. (2023)
  Storage.OPEX.ann <- Storage.Inv*Storage.OPEX.pct #EUR/year
  
  ### Offshore Pipeline
  Pipeline.Capacity <- 1000 #MW of H2
  Pipeline.Inv <- PIPE.price*dist.km*Pipeline.Capacity #EUR
  Pipeline.MEUR_km <- (Pipeline.Inv/1000000)/dist.km #MEUR/km
  Pipeline.OPEX.pct <- 0.01
  Pipeline.OPEX.ann <- Pipeline.Inv*Pipeline.OPEX.pct #EUR/year
  Pipeline.eff.pct <- 1
  
  #Sums
  Total.Inv <- (Platform.Inv + Desal.Inv + PEM.Inv + Compressor.Inv + Pipeline.Inv + Storage.Inv)/1000000 #MEUR
  Ann.OPEX <- (Platform.OPEX.ann + Desal.OPEX.ann + PEM.OPEX.ann + Compressor.OPEX.ann + Storage.OPEX.ann + Pipeline.OPEX.ann)/1000000 #MEUR/year
  
  Ann.EL <- plant.MW*8760*cf #MWh/year
  Cost.EL <- Ann.EL*Elec.Price/1000000 #MEUR/year
  
  Tot.OPEX <- Ann.OPEX + Cost.EL #MEUR/year
  
  Ann.H2.gross <- (Ann.EL/H2.LHV)*PEM.eff.pct #tonne H2/year
  Eff.check <- (Ann.EL*1000)/(Ann.H2.gross*1000) #kWh/kg. Should be in the range of 42-73
  Ann.H2.net <- Ann.H2.gross*(Compressor.eff.pct*Pipeline.eff.pct*Desal.eff.pct) #tonne H2/year
  
  Tot.Eff <- Ann.H2.net/(Ann.EL/H2.LHV) #percent. around 60-64 is expected. should not exceed the efficiency of the PEM (64%)
  
  Levelized.Cost <- LCOE(Total.Inv, Tot.OPEX, Ann.H2.net*1000, r, life, lag, CF.type) #EUR/kgH2
  Levelized.Cost.CAPEX <- LCOE(Total.Inv,OPEX = 0, ann.energy = Ann.H2.net*1000, r, life, lag, CF.type) + LCOH.Desal
  Levelized.Cost.OPEX <- LCOE(CAPEX = 0, OPEX = Ann.OPEX, ann.energy = Ann.H2.net*1000, r, life, lag, CF.type)
  Levelized.Cost.EL <- LCOE(CAPEX = 0, OPEX = Cost.EL, ann.energy = Ann.H2.net*1000, r, life, lag, CF.type)
  
  return(data.frame(Investment = Total.Inv, Pipe.MEUR_km = Pipeline.MEUR_km, OPEX = Ann.OPEX, LCOE.tot = Levelized.Cost, LCOE.CAPEX = Levelized.Cost.CAPEX, LCOE.OPEX = Levelized.Cost.OPEX, LCOE.EL = Levelized.Cost.EL, Efficiency = Tot.Eff, H2_tH2 = Ann.H2.net)) 
}

```

```{r Topology C: Offshore Electrolysis and storage, H2 ships to shore and storage}
Topology_C <- function(dist.km, plant.MW, cf = 0.5, EL.price = 35, PEM.price = 1926000, SHIP.price = 43000000, PEM.eff = 0.642, r = 0.052, life = 25, lag = 3, CF.type = 2) { 
  
  H2.LHV <- 33.33 #kWh/kg or MWh/tonne 

  ### Price of Energy (Assume it's just bought from a plant)
  Elec.Price <- EL.price #EUR/MWh. From IEA (2019) figure 7. 70% of the blue bar to exclude transmission
  
  ### Offshore Substation Platform
  # Platform.Inv <- 110000*plant.MW #EUR
  Platform.Inv <- 5840000 #EUR/platform. Assume one platform
  Platform.OPEX.pct <- 0.005 #% of investment
  Platform.OPEX.ann <- Platform.Inv*Platform.OPEX.pct #EUR/year
  
  ### Offshore Electrolyzer (PEM)
  PEM.Inv <- PEM.price*plant.MW #EUR
  PEM.OPEX.pct <- 0.015
  PEM.OPEX.ann <- PEM.Inv*PEM.OPEX.pct #EUR/year
  PEM.eff.pct <- PEM.eff #% LHV 
  
  ### Offshore Desalination. Need 
  Desal.Inv <- 0*plant.MW #19260 #EUR. Take as 1% of the electrolyzer cost
  Desal.OPEX.pct <- 0 #CHECK
  Desal.OPEX.ann <- Desal.Inv*Desal.OPEX.pct #EUR/year
  Desal.eff.pct <- 1 #CHECK. Not used yet
  LCOH.Desal <- 0.04 #EUR/kgH2. ranges from 0.01 - 0.04 according to Megan Mauter email and IEA (2019) Future of Hydrogen Report.
  
  ### Offshore Liquefication. 
  Liquefication.Inv <- 1300*plant.MW #EUR. 900-2000 USD/kW according to Kormer (2015)
  Liquefication.OPEX.pct <- 0.03 #3-5% of investment according to https://link.springer.com/chapter/10.1007/978-3-030-86884-0_2
  Liquefication.OPEX.ann <- Liquefication.Inv*Liquefication.OPEX.pct #EUR/year
  Liquefication.eff.pct <- 0.7 #% according to Kormer (2015)
  
  ### Offshore Energy Storage (battery or fuel cell for black start). Need
  ELStorage.MW <- 0 #MW of battery needed. CHECK, how to estimate this?
  ELStorage.Inv <- 1000 #EUR/kW of battery needed. EIA Source for 1-hr battery pack: https://www.eia.gov/todayinenergy/detail.php?id=45596
  ELStorage.Inv <- 1000*ELStorage.MW*ELStorage.Inv #EUR 
  ELStorage.OPEX.pct <- 0.05 #Converted using the values from Dokhani et al. (2023)
  ELStorage.OPEX.ann <- ELStorage.Inv*ELStorage.OPEX.pct #EUR/year
  
  ### ONE Hydrogen Ship 
  Ship.Inv.unit <- 675000/4 #2015 EUR per tonne LH2 according to Kormer(2015)
  Ship.Cap.unit <- 280000 #cu.m 37500 of liqefied H2 according to https://www.offshore-energy.biz/c-job-lh2-europe-present-new-liquid-hydrogen-tanker-design/
  Ship.Cap.unit <- Ship.Cap.unit*1000/14.128/1000 #tonnes of LH2 in one ship capacity. 14.128 liter of liquid H2 = 1 kg of H2 according to http://www.uigi.com/h2_conv.html
  Ship.Cost <- SHIP.price#Ship.Inv.unit*Ship.Cap.unit #EUR
  Ship.OPEX.pct <- 0.025 #According to Table 6 in https://www.jstor.org/stable/resrep31019.13?seq=5
  Ship.Speed <- 40 #km/h
  One.trip <- dist.km/Ship.Speed/24 #days for one way trip
  Ship.H2.cons <- 2.87*(Ship.Cap.unit/20000) #t LH2/h per ship consumed. According to Alkhaledi (2022) which gave 2.87t/h of green hydrogen consumption for a 20,000 tonne ship.
  LH2.boiloff <- 0.003 #0.3% per day boil-off rate in storage according to Kormer (2015)
  Ship.eff.pct <- 1 - LH2.boiloff #0.3% per day boil-off rate according to Kormer (2015)
  
  
  ### Calculate number of ships and storage size.
  # The amount of liquefied hydrogen produced per year
  Ann.EL <- plant.MW*8760*cf #MWh/year
  
  Ann.H2.gas <- (Ann.EL/H2.LHV)*PEM.eff.pct #tonne H2/year
  
  Ann.LH2 <- Ann.H2.gas*Liquefication.eff.pct #tonne LH2/year. This is how much liquefied H2 is produced and must be brought to shore per year
  
  LH2.rate <- Ann.LH2/365 #tonnes LH2/day. With this number we need to either store, or transport it to shore, and maximize the amount brought to shore, while minimizing the cost. This production rate must be equal to the shipping rate to shore, which is achieved by increasing the number of ships, otherwise, we are losing LH2.
  
  LH2.Ship.rate <- Ship.Cap.unit/(One.trip*2) #tonnes LH2/day delivered.
  N.ships <- ceiling(LH2.rate/LH2.Ship.rate)
  N.tot <- Ann.LH2/Ship.Cap.unit #Total number of trips per year needed to deliver the generated LH2 to shore
  
  Fill.time <- Ship.Cap.unit/LH2.rate #days to fill a tank
  
  if(N.ships == 1) { #in this case, we would need some storage at the plant
    t.store <- One.trip*2 + 1 #days for a ship to get back to the plant. Assumes 1 full day at port. This is how much time there would not be a ship at the plant for.
    LH2Storage.Capacity <- LH2.rate*t.store #tonnes LH2 storage capacity needed as the one ship goes to shore and back.
  } else{
    LH2Storage.Capacity <- 0
  }
  
  loss.per.trip <- One.trip*LH2.boiloff #tonnes LH2 lost from production until arrival to shore per trip
  Loss.LH2 <- loss.per.trip*N.tot #tonnes LH2 lost per year from plant to shore.
  Fuel.LH2 <- Ship.H2.cons*One.trip*N.tot #tonnes LH2 consumed per year
  
  
  ### Ship CAPEX and OPEX
  Ship.Inv <- N.ships*Ship.Cost #EUR
  Ship.OPEX.ann <- Ship.Inv*Ship.OPEX.pct #EUR/year
  
  ### Offshore Liquid H2 Storage
  LH2Storage.Cost <- 720*H2.LHV #EUR/tonne. 800-10000 2015USD/MWh according to Kormer (2015). 0.9 2015EUR = 1 2015USD
  LH2Storage.Inv <- LH2Storage.Cost*LH2Storage.Capacity #EUR
  LH2Storage.OPEX.pct <- 0.01 #CHECK
  LH2Storage.OPEX.ann <- LH2Storage.Inv*LH2Storage.OPEX.pct #EUR/year

  #Sums
  Total.Inv <- (Platform.Inv + Desal.Inv + PEM.Inv + Liquefication.Inv + LH2Storage.Inv + ELStorage.Inv + Ship.Inv)/1000000 #MEUR
  Ancillary.Inv <- (Platform.Inv + Desal.Inv + PEM.Inv + Liquefication.Inv + LH2Storage.Inv + ELStorage.Inv)/1000000 #MEUR
  Ann.OPEX <- (Platform.OPEX.ann + Desal.OPEX.ann + PEM.OPEX.ann + Liquefication.OPEX.ann + LH2Storage.OPEX.ann + ELStorage.OPEX.ann + Ship.OPEX.ann)/1000000 #MEUR/year
  
  Cost.EL <- Ann.EL*Elec.Price/1000000 #MEUR/year. paying for electricity coming off the plant
  
  Tot.OPEX <- Ann.OPEX + Cost.EL #MEUR/year
  
  Eff.check <- (Ann.EL*1000)/(Ann.H2.gas*1000) #kWh/kg. Should be in the range of 42-73
  Ann.LH2.net <- Ann.LH2 - Loss.LH2 - Fuel.LH2 #tonne H2/year
  
  Tot.Eff <- Ann.LH2.net/(Ann.EL/H2.LHV) #percent. around 60-64 is expected. should not exceed the efficiency of the PEM (64%)
  
  Levelized.Cost <- LCOE(Total.Inv, Tot.OPEX, Ann.LH2.net*1000, r, life, lag, CF.type) #EUR/kgH2
  Levelized.Cost.CAPEX <- LCOE(Total.Inv,OPEX = 0, ann.energy = Ann.LH2.net*1000, r, life, lag, CF.type) + LCOH.Desal
  Levelized.Cost.SHIP <- LCOE(Ship.Inv/1000000, OPEX = 0, ann.energy = Ann.LH2.net*1000, r, life, lag, CF.type)
  Levelized.Cost.ELPLANT <- LCOE(Ancillary.Inv, OPEX = 0, ann.energy = Ann.LH2.net*1000, r, life, lag, CF.type)
  Levelized.Cost.OPEX <- LCOE(CAPEX = 0, OPEX = Ann.OPEX, ann.energy = Ann.LH2.net*1000, r, life, lag, CF.type)
  Levelized.Cost.EL <- LCOE(CAPEX = 0, OPEX = Cost.EL, ann.energy = Ann.LH2.net*1000, r, life, lag, CF.type)
  
  return(data.frame(Investment = Total.Inv, N.Ships = N.ships, Storage_tLH2 = LH2Storage.Capacity, OPEX = Ann.OPEX, LCOE.tot = Levelized.Cost, LCOE.CAPEX = Levelized.Cost.CAPEX, LCOE.OPEX = Levelized.Cost.OPEX, LCOE.EL = Levelized.Cost.EL, Efficiency = Tot.Eff, H2_tLH2 = Ann.LH2.net)) 
}


```

```{r FUNCTIONS: Export Cable Functions - HVDC}
###HVDC Calculations
HVDC.Cables <- read.csv("C:/Users/Rudolph/Desktop/Rudolph/0 - CMU - Portugal PhD Files/0 - Research/Transmission Challenges - Offshore Wind/HVDC_Cable_Data.csv")

HVDC.Cables <- HVDC.Cables %>%
  rename(Voltage.kV = ï..Voltage.kV) %>%
  mutate(Circ.Capability.MW = 4*Voltage.kV*Current.A/1000) %>% #a circuit will have two lines. CHECK THIS
  mutate(Cost.EURkm = Cost.GBPkm*1.16) %>% #conversion as of 10/6/23
  mutate(Cost.EURMW_km = Cost.EURkm/Circ.Capability.MW)
HVDC.Cables <- setDT(HVDC.Cables)

HVDC.Terminal.Cost <- function(S_MVA, num, Fix = Fix.HVDC, Var = Var.HVDC) {
  offshore.SS.cost <- Fix + (1 + f_t * (num-2))*Var*S_MVA #in USD
  onshore.SS.cost <- 0.08148*(S_MVA)*1000000*GBP.USD #in USD
  Terminal.Cost <- offshore.SS.cost + onshore.SS.cost
  return(Terminal.Cost/1000000) #returns value in MUSD
  
}

#end-to-end efficiency
HVDC.Eff <- function(l_c, S_MVA, V_cn, r_c, n_c, pf = 1, eta.off.c = 1) { #km,MVA,kV,Ohm/km,num parallel circuits
  A <- (S_MVA*pf*eta.off.c)/V_cn^2
  B <- (r_c * l_c)/(2*n_c)
  eta.transmission <- 1 - (A*B)
  return(eta.transmission) #returns a ratio value
}

#HVDC
#note spacing comes from US DOI - Bureau of Safety and Environmental Enforcement. (2014). Offshore Wind Submarine Cable Spacing Guidance.
HVDC.System <- function(plant.MW, dist.km, spacing = 0.06, w.cost = 1, w.eta = 0, w.area = 0) {
  HVDC.dt = copy(HVDC.Cables) #Create a copy of the base Cables Data
  
  HVDC.dt[ , N.Sets := ceiling(plant.MW/Circ.Capability.MW)]
  HVDC.dt[ , Cable.Cost.MUSD := mapply(Cable.Cost,unit.cost = .(Cost.GBPkm), dist.km, num = .(N.Sets*2))]
  HVDC.dt[ , Terminal.Cost.MUSD := mapply(HVDC.Terminal.Cost, S_MVA=plant.MW, num = .(N.Sets))]
  HVDC.dt[ , Total.Cost.MUSD := Cable.Cost.MUSD + Terminal.Cost.MUSD]
  HVDC.dt[ , Eta := mapply(HVDC.Eff, dist.km, plant.MW, .(Voltage.kV),.(Resistance.Ohkm),.(N.Sets))]
  HVDC.dt[ , Area.km2 := dist.km*(N.Sets+1)*spacing] #area of seabed buffer needed
  HVDC.dt[ , Total.Cost.NORM := ifelse(sum(!is.na(Total.Cost.MUSD))>0, Total.Cost.MUSD/max(Total.Cost.MUSD, na.rm = TRUE),NA)]
  HVDC.dt[ , Eta.NORM := ifelse(sum(!is.na(Eta))>0,Eta/max(Eta, na.rm = TRUE),NA)]
  HVDC.dt[ , Area.NORM := ifelse(sum(!is.na(Area.km2))>0,Area.km2/max(Area.km2, na.rm = TRUE),NA)]
  HVDC.dt[ , SCORE := w.cost*(1-Total.Cost.NORM) + w.eta*Eta.NORM + w.area*(1-Area.NORM)]

  HVDC.dt <- HVDC.dt[order(-SCORE)]

  return(HVDC.dt[1,]) #returns an ordered dataframe, so the best option is the first
}

#### Function to add HV Cable metrics
Add.HV.System.Metrics <- function(DT, plant.size.MW, w.cost = 0.5,w.eta = 0.5, w.area = 0) { #takes the data table as an input

  #Calculate HVDC Metrics for best outcome
  HVDC.OUTPUT <- as.data.table(t(mapply(FUN = HVDC.System, dist.km = DT$Shore_dist ,plant.MW = plant.size.MW, w.cost, w.eta, w.area)))

  HVDC.OUTPUT <- setDT(HVDC.OUTPUT)

  DT[ , ':=' (Plant.seabed.cable.DC = unlist(HVDC.OUTPUT[ , "Area.km2"]),
              Plant.cost.export.DC = unlist(HVDC.OUTPUT[ , "Total.Cost.MUSD"]),
              Plant.efficiency.DC = unlist(HVDC.OUTPUT[ , "Eta"]))]

  rm(HVDC.OUTPUT) #Clean up some memory

  return(DT)
}
```

```{r FUNCTION: Run all topologies}
Calc.Topologies <- function(PLANT = 1000, EL.P = 33, CF = 0.5, CURT = 0.05, PEM.P = 1519000, SHIP.P = 43000000, PIPE.P = 615, PEM.EFF = 0.642, DISC = 0.052, LAG = 3, CF.T = 2) {
  
  MJ.kWh <- 3.6 #energy content of electricity
  MJ.kgH2 <- 120 #energy content of hydrogen
  
  max.dist <- 2700 #kilometers. 2,700km is the distance to point Nemo, which is the farthest ocean point from any shore.

  dist.V <- seq(0, max.dist, by = 100)
  # depth.V <- seq(1, max.depth, by = 1)
  
  # dist.depth <- expand.grid(dist.V, max.depth.V) #long matrix form
  Result.DF <- data.frame(distance_km = integer(),
                          distance_factor = factor(),
                          Topology = factor(),
                          TopologyA_EUR.MWh = double(),
                          TopologyB_EUR.kgH2 = double(),
                          TopologyC_EUR.kgLH2 = double(),
                          TopologyA_EUR.MJ = double(),
                          TopologyB_EUR.MJ = double(),
                          TopologyC_EUR.MJ = double(),
                          TopologyA_LCOE.EL = double(),
                          TopologyB_LCOE.EL = double(),
                          TopologyC_LCOE.EL = double(),
                          TopologyA_LCOE.CAPEX = double(),
                          TopologyB_LCOE.CAPEX = double(),
                          TopologyC_LCOE.CAPEX = double(),
                          TopologyA_LCOE.OPEX = double(),
                          TopologyB_LCOE.OPEX = double(),
                          TopologyC_LCOE.OPEX = double())
  
  
  for(dist in dist.V) {
    result.A <- Topology_A(dist.km = dist, plant.MW = PLANT, cf = CF, EL.price = EL.P, r = DISC, curtailment = CURT, interconnection = LAG, CF.type = CF.T)
    result.B <- Topology_B(dist.km = dist, plant.MW = PLANT, cf = CF, EL.price = EL.P, PEM.price = PEM.P, PIPE.price = PIPE.P, PEM.eff = PEM.EFF, r = DISC, lag = LAG, CF.type = CF.T)
    result.C <- Topology_C(dist.km = dist, plant.MW = PLANT, cf = CF, EL.price = EL.P, PEM.price = PEM.P, SHIP.price = SHIP.P, PEM.eff = PEM.EFF, r = DISC, lag = LAG, CF.type = CF.T)
    
    result.A.LCOE <- result.A$LCOE.tot/1000 #in EUR/kWh
    result.B.LCOE <- result.B$LCOE.tot #in EUR/kgH2
    result.C.LCOE <- result.C$LCOE.tot #in EUR/kgH2
    
    result.A.trans <- result.A.LCOE/MJ.kWh #in EUR/MJ
    result.B.trans <- result.B.LCOE/MJ.kgH2 #in EUR/MJ
    result.C.trans <- result.C.LCOE/MJ.kgH2 #in EUR/MJ
    
    result.A.LCOE.EL <- result.A$LCOE.EL/1000 #in EUR/kWh
    result.B.LCOE.EL <- result.B$LCOE.EL #in EUR/kgH2
    result.C.LCOE.EL <- result.C$LCOE.EL #in EUR/kgH2
    
    result.A.LCOE.CAPEX <- result.A$LCOE.CAPEX/1000 #in EUR/kWh
    result.B.LCOE.CAPEX <- result.B$LCOE.CAPEX #in EUR/kgH2
    result.C.LCOE.CAPEX <- result.C$LCOE.CAPEX #in EUR/kgH2
    
    result.A.LCOE.OPEX <- result.A$LCOE.OPEX/1000 #in EUR/kWh
    result.B.LCOE.OPEX <- result.B$LCOE.OPEX #in EUR/kgH2
    result.C.LCOE.OPEX <- result.C$LCOE.OPEX #in EUR/kgH2
    
    #levelized profit of energy to account for different markets between electricity and hydrogen
    # result.A.LPOE <- result.A.LCOE - 
    
    
    this.df <- data.frame(distance_km = dist,
                          distance_factor = dist,
                          TopologyA_EUR.kWh = result.A.LCOE,
                          TopologyB_EUR.kgH2 = result.B.LCOE,
                          TopologyC_EUR.kgLH2 = result.C.LCOE,
                          TopologyA_EUR.MJ = result.A.trans,
                          TopologyB_EUR.MJ = result.B.trans,
                          TopologyC_EUR.MJ = result.C.trans,
                          TopologyA_LCOE.EL = result.A.LCOE.EL,
                          TopologyB_LCOE.EL = result.B.LCOE.EL,
                          TopologyC_LCOE.EL = result.C.LCOE.EL,
                          TopologyA_LCOE.CAPEX = result.A.LCOE.CAPEX,
                          TopologyB_LCOE.CAPEX = result.B.LCOE.CAPEX,
                          TopologyC_LCOE.CAPEX = result.C.LCOE.CAPEX,
                          TopologyA_LCOE.OPEX = result.A.LCOE.OPEX,
                          TopologyB_LCOE.OPEX = result.B.LCOE.OPEX,
                          TopologyC_LCOE.OPEX = result.C.LCOE.OPEX)
    Result.DF <- rbind(Result.DF,this.df)
  }
  return(Result.DF)
}
```

```{r FUNCTION: Run all topologies, only for fixed distances to check difference between topologies}
Calc.Topologies.Stationary <- function(PLANT = 1000, DIST = 20, EL.P = 33, CF = 0.5, CURT = 0.05, PEM.P = 1519000, SHIP.P = 43000000, PIPE.P = 615, PEM.EFF = 0.642, DISC = 0.052, LAG = 3, CF.T = 2) {
  
  MJ.kWh <- 3.6 #energy content of electricity
  MJ.kgH2 <- 120 #energy content of hydrogen
    
  result.A <- Topology_A(dist.km = DIST, plant.MW = PLANT, cf = CF, EL.price = EL.P, r = DISC, curtailment = CURT, interconnection = LAG, CF.type = CF.T)
  result.B <- Topology_B(dist.km = DIST, plant.MW = PLANT, cf = CF, EL.price = EL.P, PEM.price = PEM.P, PIPE.price = PIPE.P, PEM.eff = PEM.EFF, r = DISC, lag = LAG, CF.type = CF.T)
  result.C <- Topology_C(dist.km = DIST, plant.MW = PLANT, cf = CF, EL.price = EL.P, PEM.price = PEM.P, SHIP.price = SHIP.P, PEM.eff = PEM.EFF, r = DISC, lag = LAG, CF.type = CF.T)
  
  result.A.LCOE <- result.A$LCOE.tot/1000 #in EUR/kWh
  result.B.LCOE <- result.B$LCOE.tot #in EUR/kgH2
  result.C.LCOE <- result.C$LCOE.tot #in EUR/kgH2
    
  result.A.trans <- result.A.LCOE/MJ.kWh #in EUR/MJ
  result.B.trans <- result.B.LCOE/MJ.kgH2 #in EUR/MJ
  result.C.trans <- result.C.LCOE/MJ.kgH2 #in EUR/MJ
  
  result.A.LCOE.EL <- result.A$LCOE.EL/1000 #in EUR/kWh
  result.B.LCOE.EL <- result.B$LCOE.EL #in EUR/kgH2
  result.C.LCOE.EL <- result.C$LCOE.EL #in EUR/kgH2
  
  result.A.LCOE.CAPEX <- result.A$LCOE.CAPEX/1000 #in EUR/kWh
  result.B.LCOE.CAPEX <- result.B$LCOE.CAPEX #in EUR/kgH2
  result.C.LCOE.CAPEX <- result.C$LCOE.CAPEX #in EUR/kgH2
  
  result.A.LCOE.OPEX <- result.A$LCOE.OPEX/1000 #in EUR/kWh
  result.B.LCOE.OPEX <- result.B$LCOE.OPEX #in EUR/kgH2
  result.C.LCOE.OPEX <- result.C$LCOE.OPEX #in EUR/kgH2
  
  #levelized profit of energy to account for different markets between electricity and hydrogen
  # result.A.LPOE <- result.A.LCOE - 
  
  
  Result.DF <- data.frame(distance_km = dist,
                         distance_factor = dist,
                         TopologyA_EUR.kWh = result.A.LCOE,
                         TopologyB_EUR.kgH2 = result.B.LCOE,
                         TopologyC_EUR.kgLH2 = result.C.LCOE,
                         TopologyA_EUR.MJ = result.A.trans,
                         TopologyB_EUR.MJ = result.B.trans,
                         TopologyC_EUR.MJ = result.C.trans,
                         TopologyA_LCOE.EL = result.A.LCOE.EL,
                         TopologyB_LCOE.EL = result.B.LCOE.EL,
                         TopologyC_LCOE.EL = result.C.LCOE.EL,
                         TopologyA_LCOE.CAPEX = result.A.LCOE.CAPEX,
                         TopologyB_LCOE.CAPEX = result.B.LCOE.CAPEX,
                         TopologyC_LCOE.CAPEX = result.C.LCOE.CAPEX,
                         TopologyA_LCOE.OPEX = result.A.LCOE.OPEX,
                         TopologyB_LCOE.OPEX = result.B.LCOE.OPEX,
                         TopologyC_LCOE.OPEX = result.C.LCOE.OPEX,
                         DIFF.AC = result.C.trans - result.A.trans,
                         DIFF.AB = result.B.trans - result.A.trans)

  return(Result.DF)
}
```

#Part 1
##Examine the impact of different lag times on project economics for Topology A. What is the LCOE for 0,1,...,10 year lags?
```{r Visual of only Topology A}
Result.A.0 <- Calc.Topologies(LAG = 0, PLANT = 1000)
Result.A.3 <- Calc.Topologies(LAG = 3, PLANT = 1000)
Result.A.6 <- Calc.Topologies(LAG = 6, PLANT = 1000)
Result.A.9 <- Calc.Topologies(LAG = 9, PLANT = 1000)
Result.A.12 <- Calc.Topologies(LAG = 12, PLANT = 1000)
Result.A.15 <- Calc.Topologies(LAG = 15, PLANT = 1000)
Result.A.18 <- Calc.Topologies(LAG = 18, PLANT = 1000)

plot(x = Result.A.3$distance_km, y = Result.A.3$TopologyA_EUR.kWh * 100, type = 'b', pch = 19, col = 'orange', ylim = c(0,40), las = 1, xaxs = 'i', yaxs = 'i', xlab = "Distance from Shore [km]", ylab = "LCOE [EURcent/kWh]")
polygon(x = c(Result.A.18$distance_km,rev(Result.A.18$distance_km)),
        y = c(Result.A.18$TopologyA_EUR.kWh*100,rev(Result.A.0$TopologyA_EUR.kWh*100)), 
        col = rgb(255/255,165/255,0,0.3), border = NA)
abline(h = 6.6, lty = 2, col = 'black') #low end of offshore wind LCOE according to Lazard (2023)
abline(h = 12.9, lty = 2, col = 'black') #low end of offshore wind LCOE according to Lazard (2023)
# abline(v = 370, col = 'red')
```


```{r Functions to calculate lag value}
Lag.Value <- function(Dist.km, Plant.MW, Type) {
  if(Type == 4) stop("use function Lag.Value.4")
  Result.DF <- data.frame(lag.years = integer(), LCOE = double())
  for(i in 0:19) {
    result <- Topology_A(Dist.km, Plant.MW, curtailment = 0.05, interconnection = i, CF.type = Type)$LCOE.tot
    result.i <- data.frame(lag.years = i, LCOE = result)
    Result.DF <- bind_rows(Result.DF, result.i)
    }
  Result.DF$LCOE.diff <- Result.DF$LCOE - lag(Result.DF$LCOE)
  return(Result.DF)
}

Lag.Value.4 <- function(Dist.km, Plant.MW, n = 10000) { #for randomly distributed payments, run the LCOE calculation many times
  Result.DF <- data.frame(lag.years = integer(), LCOE = double())
  for(i in 0:19) {
    result <- replicate(n, Topology_A(Dist.km, Plant.MW, curtailment = 0.05, interconnection = i, CF.type = 4)$LCOE.tot) #calculate the LCOE n times
    result <- mean(result) #take the mean LCOE result
    result.i <- data.frame(lag.years = i, LCOE = result)
    Result.DF <- bind_rows(Result.DF, result.i)
  }
  Result.DF$LCOE.diff <- Result.DF$LCOE - lag(Result.DF$LCOE)
  return(Result.DF)
}
```


```{r Results}
RES.1 <- Lag.Value(20, 1000, 1)
RES.2 <- Lag.Value(20, 1000, 2)
RES.3 <- Lag.Value(20, 1000, 3)
RES.4 <- Lag.Value.4(20, 1000, n = 100)
```

```{r VISUALIZE Lag}
plot(x = RES.2$lag.years, y = RES.2$LCOE, pch = 19, type = 'b', xlim = c(0,15), ylim = c(55,80),
     xlab = "Years of development", ylab = "LCOE [EUR/MWh]",
     las = 1, xaxs = 'i', yaxs = 'i')
points(x = RES.1$lag.years, y = RES.1$LCOE, pch = 19, type = 'b', col = 'blue')
# points(x = RES.2$lag.years, y = RES.2$LCOE, pch = 19, type = 'b', col = 'green')
points(x = RES.3$lag.years, y = RES.3$LCOE, pch = 19, type = 'b', col = 'orange')
points(x = RES.4$lag.years, y = RES.4$LCOE, pch = 19, type = 'b', col = 'red')
polygon(x = c(2,4,4,2), y = c(0,0,200,200), col = rgb(255/255,128/255,0,0.3), border = FALSE) #typical construction time
polygon(x = c(7,11,11,7), y = c(0,0,200,200), col = rgb(0/255,153/255,0,0.3), border = FALSE) #typical deployment time
legend('topleft', legend = c("Worst Case", "Levelized Case","Graduated Case","Randomized Case"),
       col = c('blue','black','orange','red'), pch = 19, lty = 1, cex = 0.8)
```

```{r SENSITIVITY ANALYSIS ON CF TYPE: CALCULATE mean}
mean.1 <- mean(RES.1$LCOE.diff, na.rm = TRUE)
mean.2 <- mean(RES.2$LCOE.diff, na.rm = TRUE)
mean.3 <- mean(RES.3$LCOE.diff, na.rm = TRUE)
mean.4 <- mean(RES.4$LCOE.diff, na.rm = TRUE)
```



```{r SENSITIVITY ANALYSIS ON Topology A: discount rate, years of lag, project size, distance to shore, electricity cost, ITC}
Baseline <- Topology_A(dist.km = 20, 
                       plant.MW = 1000, 
                       cf = 0.52, 
                       EL.price = 33, 
                       r = 0.052, 
                       life = 25, 
                       curtailment = 0.05, 
                       interconnection = 10, 
                       CF.type = 2)$LCOE.tot #in EUR/MWh. 61.63
#Discount rate
low.r <- 0.02
high.r <- 0.1

(Low.r <- Topology_A(dist.km = 20, 
                     plant.MW = 1000, 
                     cf = 0.52, 
                     EL.price = 33, 
                     r = low.r, 
                     life = 25, 
                     curtailment = 0.05, 
                     interconnection = 10, 
                     CF.type = 2)$LCOE.tot)

(High.r <- Topology_A(dist.km = 20, 
                      plant.MW = 1000, 
                      cf = 0.52, 
                      EL.price = 33, 
                      r = high.r, 
                      life = 25, 
                      curtailment = 0.05, 
                      interconnection = 10, 
                      CF.type = 2)$LCOE.tot)

#years of lag
low.y <- 3
high.y = 18

(Low.y <- Topology_A(dist.km = 20, 
                     plant.MW = 1000, 
                     cf = 0.52, 
                     EL.price = 33, 
                     r = 0.052, 
                     life = 25, 
                     curtailment = 0.05, 
                     interconnection = low.y, 
                     CF.type = 2)$LCOE.tot)

(High.y <- Topology_A(dist.km = 20, 
                      plant.MW = 1000, 
                      cf = 0.52, 
                      EL.price = 33, 
                      r = 0.052, 
                      life = 25, 
                      curtailment = 0.05, 
                      interconnection = high.y, 
                      CF.type = 2)$LCOE.tot)
#project size
low.p <- 100
high.p <- 2000

(Low.p <- Topology_A(dist.km = 20, 
                     plant.MW = low.p, 
                     cf = 0.52, 
                     EL.price = 33, 
                     r = 0.052, 
                     life = 25, 
                     curtailment = 0.05, 
                     interconnection = 10, 
                     CF.type = 2)$LCOE.tot)

(High.p <- Topology_A(dist.km = 20, 
                      plant.MW = high.p, 
                      cf = 0.52, 
                      EL.price = 33, 
                      r = 0.052, 
                      life = 25, 
                      curtailment = 0.05, 
                      interconnection = 10, 
                      CF.type = 2)$LCOE.tot)
#distance to shore
low.d <- 5
high.d <- 200

(Low.d <- Topology_A(dist.km = low.d, 
                     plant.MW = 1000, 
                     cf = 0.52, 
                     EL.price = 33, 
                     r = 0.052, 
                     life = 25, 
                     curtailment = 0.05, 
                     interconnection = 10, 
                     CF.type = 2)$LCOE.tot)

(High.d <- Topology_A(dist.km = high.d, 
                      plant.MW = 1000, 
                      cf = 0.52, 
                      EL.price = 33, 
                      r = 0.052, 
                      life = 25, 
                      curtailment = 0.05, 
                      interconnection = 10, 
                      CF.type = 2)$LCOE.tot)

#electricity cost 
low.e <- 29
high.e <- 35

(Low.e <- Topology_A(dist.km = 20, 
                     plant.MW = 1000, 
                     cf = 0.52, 
                     EL.price = low.e, 
                     r = 0.052, 
                     life = 25, 
                     curtailment = 0.05, 
                     interconnection = 10, 
                     CF.type = 2)$LCOE.tot)

(High.e <- Topology_A(dist.km = 20, 
                      plant.MW = 1000, 
                      cf = 0.52, 
                      EL.price = high.e, 
                      r = 0.052, 
                      life = 25, 
                      curtailment = 0.05, 
                      interconnection = 10, 
                      CF.type = 2)$LCOE.tot)

#ITC level {percent}
```


```{r SENSITIVITY ANALYSIS ON Topology Difference: discount rate, years of lag, project size, distance to shore, electricity cost, PEM cost, Ship Cost, Storage cost}

Baseline <- Calc.Topologies.Stationary(PLANT = 1000,
                                       DIST = 20,
                                       EL.P = 33,
                                       CURT = 0.05, 
                                       PEM.P = 1519000,
                                       SHIP.P = 43000000,
                                       PIPE.P = 615,
                                       PEM.EFF = 0.642,
                                       DISC = 0.052, 
                                       LAG = 3, 
                                       CF.T = 2) %>%
  select(TopologyA_EUR.MJ, DIFF.AC, DIFF.AB)

#Plant Size
low.p <- 100
high.p <- 2000

(Low.p <- Calc.Topologies.Stationary(PLANT = low.p,
                                     DIST = 20,
                                     EL.P = 33,
                                     CURT = 0.05, 
                                     PEM.P = 1519000,
                                     SHIP.P = 43000000,
                                     PIPE.P = 615,
                                     PEM.EFF = 0.642,
                                     DISC = 0.052, 
                                     LAG = 3, 
                                     CF.T = 2) %>%
  select(TopologyA_EUR.MJ, DIFF.AC, DIFF.AB))

(High.p <- Calc.Topologies.Stationary(PLANT = high.p,
                                      DIST = 20,
                                      EL.P = 33,
                                      CURT = 0.05, 
                                      PEM.P = 1519000,
                                      SHIP.P = 43000000,
                                      PIPE.P = 615,
                                      PEM.EFF = 0.642,
                                      DISC = 0.052, 
                                      LAG = 3, 
                                      CF.T = 2) %>%
  select(TopologyA_EUR.MJ, DIFF.AC, DIFF.AB))

#Shore distance
low.d <- 5
high.d <- 200

(Low.d <- Calc.Topologies.Stationary(PLANT = 1000,
                                     DIST = low.d,
                                     EL.P = 33,
                                     CURT = 0.05, 
                                     PEM.P = 1519000,
                                     SHIP.P = 43000000,
                                     PIPE.P = 615,
                                     PEM.EFF = 0.642,
                                     DISC = 0.052, 
                                     LAG = 3, 
                                     CF.T = 2) %>%
  select(TopologyA_EUR.MJ, DIFF.AC, DIFF.AB))

(High.d <- Calc.Topologies.Stationary(PLANT = 1000,
                                      DIST = high.d,
                                      EL.P = 33,
                                      CURT = 0.05, 
                                      PEM.P = 1519000,
                                      SHIP.P = 43000000,
                                      PIPE.P = 615,
                                      PEM.EFF = 0.642,
                                      DISC = 0.052, 
                                      LAG = 3, 
                                      CF.T = 2) %>%
  select(TopologyA_EUR.MJ, DIFF.AC, DIFF.AB))

#Electricity price
low.e <- 29
high.e <- 35

(Low.e <- Calc.Topologies.Stationary(PLANT = 1000,
                                     DIST = 20,
                                     EL.P = low.e,
                                     CURT = 0.05, 
                                     PEM.P = 1519000,
                                     SHIP.P = 43000000,
                                     PIPE.P = 615,
                                     PEM.EFF = 0.642,
                                     DISC = 0.052, 
                                     LAG = 3, 
                                     CF.T = 2) %>%
  select(TopologyA_EUR.MJ, DIFF.AC, DIFF.AB))

(High.e <- Calc.Topologies.Stationary(PLANT = 1000,
                                      DIST = 20,
                                      EL.P = high.e,
                                      CURT = 0.05, 
                                      PEM.P = 1519000,
                                      SHIP.P = 43000000,
                                      PIPE.P = 615,
                                      PEM.EFF = 0.642,
                                      DISC = 0.052, 
                                      LAG = 3, 
                                      CF.T = 2) %>%
  select(TopologyA_EUR.MJ, DIFF.AC, DIFF.AB))

#Curtailment
low.c <- 0.02
high.c <- 0.3

(Low.c <- Calc.Topologies.Stationary(PLANT = 1000,
                                     DIST = 20,
                                     EL.P = 33,
                                     CURT = low.c, 
                                     PEM.P = 1519000,
                                     SHIP.P = 43000000,
                                     PIPE.P = 615,
                                     PEM.EFF = 0.642,
                                     DISC = 0.052, 
                                     LAG = 3, 
                                     CF.T = 2) %>%
  select(TopologyA_EUR.MJ, DIFF.AC, DIFF.AB))

(High.c <- Calc.Topologies.Stationary(PLANT = 1000,
                                      DIST = 20,
                                      EL.P = 33,
                                      CURT = high.c, 
                                      PEM.P = 1519000,
                                      SHIP.P = 43000000,
                                      PIPE.P = 615,
                                      PEM.EFF = 0.642,
                                      DISC = 0.052, 
                                      LAG = 3, 
                                      CF.T = 2) %>%
  select(TopologyA_EUR.MJ, DIFF.AC, DIFF.AB))

#Electrolyzer cost
low.p <- 1198000
high.p <- 1926000

(Low.p <- Calc.Topologies.Stationary(PLANT = 1000,
                                     DIST = 20,
                                     EL.P = 33,
                                     CURT = 0.05, 
                                     PEM.P = low.p,
                                     SHIP.P = 43000000,
                                     PIPE.P = 615,
                                     PEM.EFF = 0.642,
                                     DISC = 0.052, 
                                     LAG = 3, 
                                     CF.T = 2) %>%
  select(TopologyA_EUR.MJ, DIFF.AC, DIFF.AB))

(High.p <- Calc.Topologies.Stationary(PLANT = 1000,
                                      DIST = 20,
                                      EL.P = 33,
                                      CURT = 0.05, 
                                      PEM.P = high.p,
                                      SHIP.P = 43000000,
                                      PIPE.P = 615,
                                      PEM.EFF = 0.642,
                                      DISC = 0.052, 
                                      LAG = 3, 
                                      CF.T = 2) %>%
  select(TopologyA_EUR.MJ, DIFF.AC, DIFF.AB))

#Ship cost
low.s <- 25000000
high.s <- 80000000

(Low.s <- Calc.Topologies.Stationary(PLANT = 1000,
                                     DIST = 20,
                                     EL.P = 33,
                                     CURT = 0.05, 
                                     PEM.P = 1519000,
                                     SHIP.P = low.s,
                                     PIPE.P = 615,
                                     PEM.EFF = 0.642,
                                     DISC = 0.052, 
                                     LAG = 3, 
                                     CF.T = 2) %>%
  select(TopologyA_EUR.MJ, DIFF.AC, DIFF.AB))

(High.s <- Calc.Topologies.Stationary(PLANT = 1000,
                                      DIST = 20,
                                      EL.P = 33,
                                      CURT = 0.05, 
                                      PEM.P = 1519000,
                                      SHIP.P = high.s,
                                      PIPE.P = 615,
                                      PEM.EFF = 0.642,
                                      DISC = 0.052, 
                                      LAG = 3, 
                                      CF.T = 2) %>%
  select(TopologyA_EUR.MJ, DIFF.AC, DIFF.AB))

#Pipe cost
low.l <- 500
high.l <- 700

(Low.l <- Calc.Topologies.Stationary(PLANT = 1000,
                                     DIST = 20,
                                     EL.P = 33,
                                     CURT = 0.05, 
                                     PEM.P = 1519000,
                                     SHIP.P = 43000000,
                                     PIPE.P = low.l,
                                     PEM.EFF = 0.642,
                                     DISC = 0.052, 
                                     LAG = 3, 
                                     CF.T = 2) %>%
  select(TopologyA_EUR.MJ, DIFF.AC, DIFF.AB))

(High.l <- Calc.Topologies.Stationary(PLANT = 1000,
                                      DIST = 20,
                                      EL.P = 33,
                                      CURT = 0.05, 
                                      PEM.P = 1519000,
                                      SHIP.P = 43000000,
                                      PIPE.P = high.l,
                                      PEM.EFF = 0.642,
                                      DISC = 0.052, 
                                      LAG = 3, 
                                      CF.T = 2) %>%
  select(TopologyA_EUR.MJ, DIFF.AC, DIFF.AB))

#Electrolyzer efficiency
low.n <- 0.62
high.n <- 0.7

(Low.n <- Calc.Topologies.Stationary(PLANT = 1000,
                                     DIST = 20,
                                     EL.P = 33,
                                     CURT = 0.05, 
                                     PEM.P = 1519000,
                                     SHIP.P = 43000000,
                                     PIPE.P = 615,
                                     PEM.EFF = low.n,
                                     DISC = 0.052, 
                                     LAG = 3, 
                                     CF.T = 2) %>%
  select(TopologyA_EUR.MJ, DIFF.AC, DIFF.AB))

(High.n <- Calc.Topologies.Stationary(PLANT = 1000,
                                      DIST = 20,
                                      EL.P = 33,
                                      CURT = 0.05, 
                                      PEM.P = 1519000,
                                      SHIP.P = 43000000,
                                      PIPE.P = 615,
                                      PEM.EFF = high.n,
                                      DISC = 0.052, 
                                      LAG = 3, 
                                      CF.T = 2) %>%
  select(TopologyA_EUR.MJ, DIFF.AC, DIFF.AB))

#Discount rate
low.r <- 0.02
high.r <- 0.1

(Low.r <- Calc.Topologies.Stationary(PLANT = 1000,
                                     DIST = 20,
                                     EL.P = 33,
                                     CURT = 0.05, 
                                     PEM.P = 1519000,
                                     SHIP.P = 43000000,
                                     PIPE.P = 615,
                                     PEM.EFF = 0.642,
                                     DISC = low.r, 
                                     LAG = 3, 
                                     CF.T = 2) %>%
  select(TopologyA_EUR.MJ, DIFF.AC, DIFF.AB))

(High.r <- Calc.Topologies.Stationary(PLANT = 1000,
                                      DIST = 20,
                                      EL.P = 33,
                                      CURT = 0.05, 
                                      PEM.P = 1519000,
                                      SHIP.P = 43000000,
                                      PIPE.P = 615,
                                      PEM.EFF = 0.642,
                                      DISC = high.r, 
                                      LAG = 3, 
                                      CF.T = 2) %>%
  select(TopologyA_EUR.MJ, DIFF.AC, DIFF.AB))

#Years of lag
low.y <- 3
high.y <- 18

(Low.y <- Calc.Topologies.Stationary(PLANT = 1000,
                                     DIST = 20,
                                     EL.P = 33,
                                     CURT = 0.05, 
                                     PEM.P = 1519000,
                                     SHIP.P = 43000000,
                                     PIPE.P = 615,
                                     PEM.EFF = 0.642,
                                     DISC = 0.052, 
                                     LAG = low.y, 
                                     CF.T = 2) %>%
  select(TopologyA_EUR.MJ, DIFF.AC, DIFF.AB))

(High.y <- Calc.Topologies.Stationary(PLANT = 1000,
                                      DIST = 20,
                                      EL.P = 33,
                                      CURT = 0.05, 
                                      PEM.P = 1519000,
                                      SHIP.P = 43000000,
                                      PIPE.P = 615,
                                      PEM.EFF = 0.642,
                                      DISC = 0.052, 
                                      LAG = high.y, 
                                      CF.T = 2) %>%
  select(TopologyA_EUR.MJ, DIFF.AC, DIFF.AB))

```

```{r CALCULATE Effect of ITC vs 1 year of lag reduction}
Policy.Base <- Topology_A(dist.km = 20, 
                          plant.MW = 1000, 
                          cf = 0.5, 
                          EL.price = 33, 
                          r = 0.052, 
                          life = 25, 
                          curtailment = 0.05, 
                          interconnection = 10, 
                          CF.type = 2,
                          ITC = 0)$LCOE.tot #62.64 EUR/MWh 

Policy.ITC <- Topology_A(dist.km = 20, 
                         plant.MW = 1000, 
                         cf = 0.5, 
                         EL.price = 33, 
                         r = 0.052, 
                         life = 25, 
                         curtailment = 0.05, 
                         interconnection = 10, 
                         CF.type = 2,
                         ITC = 0.026)$LCOE.tot #62.08 EUR/MWh 

Policy.LAG <- Topology_A(dist.km = 20, 
                         plant.MW = 1000, 
                         cf = 0.5, 
                         EL.price = 33, 
                         r = 0.052, 
                         life = 25, 
                         curtailment = 0.05, 
                         interconnection = 9, 
                         CF.type = 2,
                         ITC = 0)$LCOE.tot #62.06 EUR/MWh. What will it cost to reduce permitting time by 1 year?

```

#Part 2
##Calculate the regulatory difference needed for Topology C to be cheaper.

##Topology A vs. Topology C. Topology C may benefit from shorter permitting time due to less space required
```{r Results Generating}

Result.high <- Calc.Topologies(EL.P = 35, PEM.P = 1926000, LAG = 20)
Result.mid <- Calc.Topologies(EL.P = 33, PEM.P = 1519000, LAG = 3)
Result.low <- Calc.Topologies(EL.P = 29, PEM.P = 1198000, LAG = 0)

```


```{r Plot, fig.width=7}
# plot(x = Result.DF$distance_km, y = Result.DF$TopologyB_EUR.kgH2, type = 'b', pch = 19, col = 'blue', ylim = c(0,10))
# lines(x = Result.DF$distance_km, y = Result.DF$TopologyC_EUR.kgLH2, type = 'b', pch = 19, col = 'green')
# abline(v = 200, col = 'red')
MJ.kWh <- 3.6 #energy content of electricity
MJ.kgH2 <- 120 #energy content of hydrogen

axs.ticks <- c(0,0.02,0.04,0.06,0.08,0.1,0.12,0.14,0.16)

par(mar = c(5.5,12,2,2))
plot(x = Result.mid$distance_km, y = Result.mid$TopologyA_EUR.MJ, type = 'b', pch = 19, col = 'orange', ylim = c(0,0.16), las = 1, xaxs = 'i', yaxs = 'i', yaxt = 'n', xlab = "Distance from Shore [km]", ylab = "")
lines(x = Result.mid$distance_km, y = Result.mid$TopologyB_EUR.MJ, type = 'b', pch = 17, col = 'blue')
lines(x = Result.mid$distance_km, y = Result.mid$TopologyC_EUR.MJ, type = 'b', pch = 15, col = 'blue')
abline(h = 6.6/MJ.kWh, lty = 2, col = 'black') #low end of offshore wind LCOE according to Lazard (2023)
abline(h = 12.9/MJ.kWh, lty = 2, col = 'black') #low end of offshore wind LCOE according to Lazard (2023)
# lines(x = Result.high$distance_km, y = Result.high$TopologyA_EUR.MJ, type = 'l', pch = 15, col = 'orange')
polygon(x = c(Result.high$distance_km,rev(Result.high$distance_km)),
        y = c(Result.high$TopologyA_EUR.MJ,rev(Result.low$TopologyA_EUR.MJ)), 
        col = rgb(255/255,165/255,0,0.3), border = NA)
polygon(x = c(Result.high$distance_km,rev(Result.high$distance_km)),
        y = c(Result.high$TopologyB_EUR.MJ,rev(Result.low$TopologyB_EUR.MJ)),
        col = rgb(0,0,1,0.3), border = NA)
polygon(x = c(Result.high$distance_km,rev(Result.high$distance_km)),
        y = c(Result.high$TopologyC_EUR.MJ,rev(Result.low$TopologyC_EUR.MJ)), 
        col = rgb(0,0,1,0.3), border = NA)

abline(v = 370, col = 'red')
axis(side = 2, pos = 0, las = 1, at = axs.ticks, labels = axs.ticks*100) #EURcent/MJ
axis(side = 2, pos = -375, las = 1, at = axs.ticks, labels = axs.ticks*MJ.kWh*100, col = 'orange', col.axis = 'orange') #EURcent/kWh
axis(side = 2, pos = -850, las = 1, at = axs.ticks, labels = axs.ticks*MJ.kgH2, col = 'blue', col.axis = 'blue') #EUR/kgH2
mtext("EURcent/MJ", side = 2, line = 1.75)
mtext("EURcent/kWh", side = 2, line = 5.5, col = 'orange')
mtext("EUR/kgH2", side = 2, line = 8.7, col = 'blue')
# legend('bottomright', legend = c("A: HVDC","C: H2 Ships"),
#        pch = c(19,15), col = c("orange","blue"), lty = 1)

legend('topleft', legend = c("A: HVDC","B: H2 Pipelines", "C: H2 Ships"),
       pch = c(19,17,15), col = c("orange","blue","blue"), lty = 1)


```

##Topology A vs. Topology B. Topology B may benefit from no interconnection time
```{r Results Generating}

Result.mid <- Calc.Topologies(EL.P = 33, PEM.P = 1519000, LAG = 2)
Result.high <- Calc.Topologies(LAG = 10)
Result.low <- Calc.Topologies(EL.P = 29, PEM.P = 1198000, LAG = 0)

```


```{r Plot, fig.width=7}
# plot(x = Result.DF$distance_km, y = Result.DF$TopologyB_EUR.kgH2, type = 'b', pch = 19, col = 'blue', ylim = c(0,10))
# lines(x = Result.DF$distance_km, y = Result.DF$TopologyC_EUR.kgLH2, type = 'b', pch = 19, col = 'green')
# abline(v = 200, col = 'red')
MJ.kWh <- 3.6 #energy content of electricity
MJ.kgH2 <- 120 #energy content of hydrogen

axs.ticks <- c(0,0.02,0.04,0.06,0.08,0.1,0.12,0.14,0.16)

par(mar = c(5.5,12,2,2))
plot(x = Result.mid$distance_km, y = Result.mid$TopologyA_EUR.MJ, type = 'b', pch = 19, col = 'orange', ylim = c(0,0.16), las = 1, xaxs = 'i', yaxs = 'i', yaxt = 'n', xlab = "Distance from Shore [km]", ylab = "")
lines(x = Result.mid$distance_km, y = Result.mid$TopologyB_EUR.MJ, type = 'b', pch = 17, col = 'blue')
# lines(x = Result.mid$distance_km, y = Result.mid$TopologyC_EUR.MJ, type = 'b', pch = 15, col = 'blue')
# lines(x = Result.high$distance_km, y = Result.high$TopologyA_EUR.MJ, type = 'l', pch = 15, col = 'orange')
polygon(x = c(Result.high$distance_km,rev(Result.high$distance_km)),
        y = c(Result.high$TopologyA_EUR.MJ,rev(Result.low$TopologyA_EUR.MJ)), 
        col = rgb(255/255,165/255,0,0.3), border = NA)
polygon(x = c(Result.high$distance_km,rev(Result.high$distance_km)),
        y = c(Result.high$TopologyB_EUR.MJ,rev(Result.low$TopologyB_EUR.MJ)),
        col = rgb(0,0,1,0.3), border = NA)
# polygon(x = c(Result.high$distance_km,rev(Result.high$distance_km)),
#         y = c(Result.high$TopologyC_EUR.MJ,rev(Result.low$TopologyC_EUR.MJ)), 
#         col = rgb(0,0,1,0.3), border = NA)
abline(v = 370, col = 'red')
axis(side = 2, pos = 0, las = 1, at = axs.ticks, labels = axs.ticks*100) #EURcent/MJ
axis(side = 2, pos = -375, las = 1, at = axs.ticks, labels = axs.ticks*MJ.kWh*100, col = 'orange', col.axis = 'orange') #EURcent/kWh
axis(side = 2, pos = -850, las = 1, at = axs.ticks, labels = axs.ticks*MJ.kgH2, col = 'blue', col.axis = 'blue') #EUR/kgH2
mtext("EURcent/MJ", side = 2, line = 1.75)
mtext("EURcent/kWh", side = 2, line = 5.5, col = 'orange')
mtext("EUR/kgH2", side = 2, line = 8.5, col = 'blue')
legend('bottomright', legend = c("A: HVDC","B: H2 Pipelines"),
       pch = c(19,17), col = c("orange","blue"), lty = 1)


```

```{r Bar Plots}
Bars <- filter(Result.DF, distance_km == 2000)
```

```{r Results Generating small plant}

Result.mid <- Calc.Topologies(PLANT = 100, EL.P = 33, PEM.P = 1519000)
Result.high <- Calc.Topologies(PLANT = 100)
Result.low <- Calc.Topologies(PLANT = 100, EL.P = 29, PEM.P = 1198000)

```


```{r Plot, fig.width=7}
# plot(x = Result.DF$distance_km, y = Result.DF$TopologyB_EUR.kgH2, type = 'b', pch = 19, col = 'blue', ylim = c(0,10))
# lines(x = Result.DF$distance_km, y = Result.DF$TopologyC_EUR.kgLH2, type = 'b', pch = 19, col = 'green')
# abline(v = 200, col = 'red')
MJ.kWh <- 3.6 #energy content of electricity
MJ.kgH2 <- 120 #energy content of hydrogen

axs.ticks <- c(0,0.02,0.04,0.06,0.08,0.1)

par(mar = c(5.5,12,2,2))
plot(x = Result.mid$distance_km, y = Result.mid$TopologyA_EUR.MJ, type = 'b', pch = 19, col = 'orange', ylim = c(0,0.1), las = 1, xaxs = 'i', yaxs = 'i', yaxt = 'n', xlab = "Distance from Shore [km]", ylab = "")
lines(x = Result.mid$distance_km, y = Result.mid$TopologyB_EUR.MJ, type = 'b', pch = 17, col = 'blue')
lines(x = Result.mid$distance_km, y = Result.mid$TopologyC_EUR.MJ, type = 'b', pch = 15, col = 'blue')
polygon(x = c(Result.high$distance_km,rev(Result.high$distance_km)),
        y = c(Result.high$TopologyA_EUR.MJ,rev(Result.low$TopologyA_EUR.MJ)), 
        col = rgb(255/255,165/255,0,0.3), border = NA)
polygon(x = c(Result.high$distance_km,rev(Result.high$distance_km)),
        y = c(Result.high$TopologyB_EUR.MJ,rev(Result.low$TopologyB_EUR.MJ)), 
        col = rgb(0,0,1,0.3), border = NA)
polygon(x = c(Result.high$distance_km,rev(Result.high$distance_km)),
        y = c(Result.high$TopologyC_EUR.MJ,rev(Result.low$TopologyC_EUR.MJ)), 
        col = rgb(0,0,1,0.3), border = NA)
abline(v = 200, col = 'red')
axis(side = 2, pos = 0, las = 1, at = axs.ticks, labels = axs.ticks*100) #EURcent/MJ
axis(side = 2, pos = -375, las = 1, at = axs.ticks, labels = axs.ticks*MJ.kWh*100, col = 'orange', col.axis = 'orange') #EURcent/kWh
axis(side = 2, pos = -850, las = 1, at = axs.ticks, labels = axs.ticks*MJ.kgH2, col = 'blue', col.axis = 'blue') #EUR/kgH2
mtext("EURcent/MJ", side = 2, line = 1.75)
mtext("EURcent/kWh", side = 2, line = 5.5, col = 'orange')
mtext("EUR/kgH2", side = 2, line = 8.5, col = 'blue')
legend('bottomright', legend = c("A: HVDC","B: H2 Pipelines", "C: H2 Ships"),
       pch = c(19,17,15), col = c("orange","blue","blue"), lty = 1)


```

```{r Results Generating small plant}

Result.mid <- Calc.Topologies(PLANT = 10000, EL.P = 33, PEM.P = 1519000)
Result.high <- Calc.Topologies(PLANT = 10000)
Result.low <- Calc.Topologies(PLANT = 10000, EL.P = 29, PEM.P = 1198000)

```


```{r Plot, fig.width=7}
# plot(x = Result.DF$distance_km, y = Result.DF$TopologyB_EUR.kgH2, type = 'b', pch = 19, col = 'blue', ylim = c(0,10))
# lines(x = Result.DF$distance_km, y = Result.DF$TopologyC_EUR.kgLH2, type = 'b', pch = 19, col = 'green')
# abline(v = 200, col = 'red')
MJ.kWh <- 3.6 #energy content of electricity
MJ.kgH2 <- 120 #energy content of hydrogen

axs.ticks <- c(0,0.02,0.04,0.06,0.08,0.1)

par(mar = c(5.5,12,2,2))
plot(x = Result.mid$distance_km, y = Result.mid$TopologyA_EUR.MJ, type = 'b', pch = 19, col = 'orange', ylim = c(0,0.1), las = 1, xaxs = 'i', yaxs = 'i', yaxt = 'n', xlab = "Distance from Shore [km]", ylab = "")
lines(x = Result.mid$distance_km, y = Result.mid$TopologyB_EUR.MJ, type = 'b', pch = 17, col = 'blue')
lines(x = Result.mid$distance_km, y = Result.mid$TopologyC_EUR.MJ, type = 'b', pch = 15, col = 'blue')
polygon(x = c(Result.high$distance_km,rev(Result.high$distance_km)),
        y = c(Result.high$TopologyA_EUR.MJ,rev(Result.low$TopologyA_EUR.MJ)), 
        col = rgb(255/255,165/255,0,0.3), border = NA)
polygon(x = c(Result.high$distance_km,rev(Result.high$distance_km)),
        y = c(Result.high$TopologyB_EUR.MJ,rev(Result.low$TopologyB_EUR.MJ)), 
        col = rgb(0,0,1,0.3), border = NA)
polygon(x = c(Result.high$distance_km,rev(Result.high$distance_km)),
        y = c(Result.high$TopologyC_EUR.MJ,rev(Result.low$TopologyC_EUR.MJ)), 
        col = rgb(0,0,1,0.3), border = NA)
abline(v = 200, col = 'red')
axis(side = 2, pos = 0, las = 1, at = axs.ticks, labels = axs.ticks*100) #EURcent/MJ
axis(side = 2, pos = -375, las = 1, at = axs.ticks, labels = axs.ticks*MJ.kWh*100, col = 'orange', col.axis = 'orange') #EURcent/kWh
axis(side = 2, pos = -850, las = 1, at = axs.ticks, labels = axs.ticks*MJ.kgH2, col = 'blue', col.axis = 'blue') #EUR/kgH2
mtext("EURcent/MJ", side = 2, line = 1.75)
mtext("EURcent/kWh", side = 2, line = 5.5, col = 'orange')
mtext("EUR/kgH2", side = 2, line = 8.5, col = 'blue')
legend('bottomright', legend = c("A: HVDC","B: H2 Pipelines", "C: H2 Ships"),
       pch = c(19,17,15), col = c("orange","blue","blue"), lty = 1)


```



```{r Result Wide to Long}
Result.Long <- gather(Result.DF, Parameter, Value, TopologyA_EUR.kWh:TopologyC_LCOE.OPEX, factor_key = TRUE) %>%
  mutate(distance_factor = as.factor(distance_km))

Result.Long$Topology <- NA #gsub("[^ABC]?", "", Result.Long$Parameter) %>%
  #as.factor()

Result.Long$Component <- NA
Result.Long$Unit <- NA

for(row in 1:nrow(Result.Long)) {
  if(Result.Long$Parameter[row] == "TopologyA_EUR.kWh") {
    Result.Long$Topology[row] <- "A"
    Result.Long$Component[row] <- "Overall"
    Result.Long$Unit[row] <- "EUR/kWh"
  }
  if(Result.Long$Parameter[row] == "TopologyB_EUR.kgH2") {
    Result.Long$Topology[row] <- "B"
    Result.Long$Component[row] <- "Overall"
    Result.Long$Unit[row] <- "EUR/kgH2"
  }
  if(Result.Long$Parameter[row] == "TopologyC_EUR.kgLH2") {
    Result.Long$Topology[row] <- "C"
    Result.Long$Component[row] <- "Overall"
    Result.Long$Unit[row] <- "EUR/kgH2"
  }
  if(Result.Long$Parameter[row] == "TopologyA_EUR.MJ") {
    Result.Long$Topology[row] <- "A"
    Result.Long$Component[row] <- "Overall"
    Result.Long$Unit[row] <- "EUR/MJ"
  }
  if(Result.Long$Parameter[row] == "TopologyB_EUR.MJ") {
    Result.Long$Topology[row] <- "B"
    Result.Long$Component[row] <- "Overall"
    Result.Long$Unit[row] <- "EUR/MJ"
  }
  if(Result.Long$Parameter[row] == "TopologyC_EUR.MJ") {
    Result.Long$Topology[row] <- "C"
    Result.Long$Component[row] <- "Overall"
    Result.Long$Unit[row] <- "EUR/MJ"
  }
  if(Result.Long$Parameter[row] == "TopologyA_LCOE.EL") {
    Result.Long$Topology[row] <- "A"
    Result.Long$Component[row] <- "Electricity"
    Result.Long$Unit[row] <- "EUR/MJ"
  }
  if(Result.Long$Parameter[row] == "TopologyB_LCOE.EL") {
    Result.Long$Topology[row] <- "B"
    Result.Long$Component[row] <- "Electricity"
    Result.Long$Unit[row] <- "EUR/MJ"
  }
  if(Result.Long$Parameter[row] == "TopologyC_LCOE.EL") {
    Result.Long$Topology[row] <- "C"
    Result.Long$Component[row] <- "Electricity"
    Result.Long$Unit[row] <- "EUR/MJ"
  }
  if(Result.Long$Parameter[row] == "TopologyA_LCOE.CAPEX") {
    Result.Long$Topology[row] <- "A"
    Result.Long$Component[row] <- "CAPEX"
    Result.Long$Unit[row] <- "EUR/MJ"
  }
  if(Result.Long$Parameter[row] == "TopologyB_LCOE.CAPEX") {
    Result.Long$Topology[row] <- "B"
    Result.Long$Component[row] <- "CAPEX"
    Result.Long$Unit[row] <- "EUR/MJ"
  }
  if(Result.Long$Parameter[row] == "TopologyC_LCOE.CAPEX") {
    Result.Long$Topology[row] <- "C"
    Result.Long$Component[row] <- "CAPEX"
    Result.Long$Unit[row] <- "EUR/MJ"
  }
  if(Result.Long$Parameter[row] == "TopologyA_LCOE.OPEX") {
    Result.Long$Topology[row] <- "A"
    Result.Long$Component[row] <- "OPEX"
    Result.Long$Unit[row] <- "EUR/MJ"
  }
  if(Result.Long$Parameter[row] == "TopologyB_LCOE.OPEX") {
    Result.Long$Topology[row] <- "B"
    Result.Long$Component[row] <- "OPEX"
    Result.Long$Unit[row] <- "EUR/MJ"
  }
  if(Result.Long$Parameter[row] == "TopologyC_LCOE.OPEX") {
    Result.Long$Topology[row] <- "C"
    Result.Long$Component[row] <- "OPEX"
    Result.Long$Unit[row] <- "EUR/MJ"
  }
}

Result.Long$Topology <- as.factor(Result.Long$Topology)
Result.Long$Component <- as.factor(Result.Long$Component)
Result.Long$Unit <- as.factor(Result.Long$Unit)

Result.Long$Component <- relevel(Result.Long$Component, "OPEX")

```


```{r Bar Plot}
Result.Long.A <- filter(Result.Long, Topology == "A", Component != "Overall", Unit == "EUR/MJ", distance_km <= 5000)

test <- filter(Result.Long.A, distance_km == 500)
Result.Long.B <- filter(Result.Long, Topology == "B", Component != "Overall", Unit == "EUR/MJ", distance_km <= 5000)

Result.Long.C <- filter(Result.Long, Topology == "C", Component != "Overall", Unit == "EUR/MJ", distance_km <= 5000)

ggplot(Result.Long.B, aes(fill = Component, y = Value, x = distance_km)) + 
  geom_bar(position = "stack", stat = "identity") +
  labs(x = "Distance to Shore [km]", y = "LCOE [euro cents/MJ]")

```

#Part 3

##Calculate the electrolyzer cost and efficiency needed to make Topology B and C cheaper

```{r}
max.eff <- 0.94 #maximum theoretical electrolysis efficiency [source]
min.cost <- 13050000 #EUR/MW... 1400000 USD/MW PEM; 800000 USD/MW liquid alkaline [source]

#at 200nm (370km), what is the cost of electrolyzers needed to make Topology B and C cheaper than Topology A?
Baseline.A <- (Topology_A(dist.km = 370, plant.MW = 1000, interconnection = 3, curtailment = 0.1)$LCOE.tot/1000)/MJ.kWh
Result.B <- (Topology_B(dist.km = 370, plant.MW = 1000, PEM.eff = 0.77, PEM.price = min.cost, lag = 3)$LCOE.tot)/MJ.kgH2

Diff.BA <- Result.B - Baseline.A #the amount that LCOE from B exceeds the LCOE from A
result.cost.B <- min.cost #initiate the resulting cost.

while(Diff.BA >= 0) { #starting from the minimum theoretical cost, increase the PEM cost to find the switchover.
  result.cost.B <- result.cost.B - 1000 #increase the PEM unit cost by 1000 EUR/MW 
  Result.B <- Topology_B(dist.km = 370, plant.MW = 1000, PEM.eff = 0.77, PEM.price = result.cost.B, lag = 5)$LCOE.tot
  Diff.BA <- Result.B - Baseline.A
}

#compared to C
Result.C <- (Topology_C(dist.km = 370, plant.MW = 1000, PEM.eff = 0.77, PEM.price = min.cost, lag = 3))$LCOE.tot/MJ.kgH2

Diff.CA <- Result.C - Baseline.A
result.cost.C <- min.cost #initiate the resulting cost.

while(Diff.CA >= 0) { #starting from the minimum theoretical cost, increase the PEM cost to find the switchover.
  result.cost.C <- result.cost.C - 1000 #increase the PEM unit cost by 1000 EUR/MW 
  Result.C <- (Topology_C(dist.km = 370, plant.MW = 1000, PEM.eff = 0.77, PEM.price = result.cost.C, lag = 3))$LCOE.tot/MJ.kgH2
  Diff.CA <- Result.C - Baseline.A
}

#at 20km,...
Baseline.A <- (Topology_A(dist.km = 20, plant.MW = 1000, interconnection = 3, curtailment = 0.1)$LCOE.tot/1000)/MJ.kWh
Result.B <- (Topology_B(dist.km = 20, plant.MW = 1000, PEM.eff = 0.77, PEM.price = min.cost, lag = 3)$LCOE.tot)/MJ.kgH2

Diff.BA <- Result.B - Baseline.A #the amount that LCOE from B exceeds the LCOE from A
result.cost.B <- min.cost #initiate the resulting cost.

while(Diff.BA >= 0) { #starting from the minimum theoretical cost, increase the PEM cost to find the switchover.
  result.cost.B <- result.cost.B - 1000 #increase the PEM unit cost by 1000 EUR/MW 
  Result.B <- Topology_B(dist.km = 20, plant.MW = 1000, PEM.eff = 0.77, PEM.price = result.cost.B, lag = 5)$LCOE.tot
  Diff.BA <- Result.B - Baseline.A
}

#compared to C
Result.C <- (Topology_C(dist.km = 20, plant.MW = 1000, PEM.eff = 0.77, PEM.price = min.cost, lag = 3))$LCOE.tot/MJ.kgH2

Diff.CA <- Result.C - Baseline.A
result.cost.C <- min.cost #initiate the resulting cost.

while(Diff.CA >= 0) { #starting from the minimum theoretical cost, increase the PEM cost to find the switchover.
  result.cost.C <- result.cost.C - 1000 #increase the PEM unit cost by 1000 EUR/MW 
  Result.C <- (Topology_C(dist.km = 20, plant.MW = 1000, PEM.eff = 0.77, PEM.price = result.cost.C, lag = 3))$LCOE.tot/MJ.kgH2
  Diff.CA <- Result.C - Baseline.A
}

```

